%-------------------------
% Resume in Latex
%-------------------------
\input{config} % Includes the configuration file

%---- Defining Resume Information ----

\newcommand{\name}{Nilton Aguiar dos Santos} % My Name
\newcommand{\course}{Computer Engineering} % My Course
\newcommand{\phone}{+55 (65) 99278-5635} % My Phone Number
\newcommand{\emaila}{nilton.naab@gmail.com} % My Email
\newcommand{\github}{https://github.com/notNilton} % My Github
\newcommand{\linkedin}{https://www.linkedin.com/in/notnilton/} % My Linkedin
\newcommand{\portfolio}{https://github.com/notNilton} % My Portfolio


\begin{document}
\fontfamily{cmr}\selectfont

%----------HEADER-----------------
{
\begin{tabularx}{\linewidth}{L r} \\
    \textbf{\Large \name} & {\raisebox{0.0\height}{\footnotesize \faPhone}\ \phone}
    \\
    {Computer Engineer}
    &
    \href{\portfolio}{\raisebox{0.0\height}{\footnotesize \faGlobe}\ {Portfolio}}
    \\
    \href{mailto:\emaila} {\raisebox{0.0\height}{\footnotesize \faEnvelope}\ {\emaila}}
    \href{\linkedin}{\raisebox{0.0\height}{\footnotesize \faLinkedin}\ {LinkedIn} }
    \href{\github}{\raisebox{0.0\height}{\footnotesize \faGithub}\ {GitHub} }
\end{tabularx}
}

\section{\textbf{Education}}
    \resumeSubHeadingListStart
    \resumeSubheading
    {Bachelor’s in Computer Engineering}{}
    {Federal University of Mato Grosso, Brazil}{2020-25}
    \resumeSubHeadingListEnd
\vspace{-5.5mm}

%-----------PERSONAL PROJECTS-----------------
\section{\textbf{Personal Projects}}
\resumeSubHeadingListStart
    \resumeProject
      { RADARE - \textit{Reconciliation and Data Analysis in a Responsive Environment}}
      {Web application based on React for data reconciliation.}
      {}

      \resumeItemListStart
        \item Industrial data reconciliation using multivariable function minimization by the Lagrange multiplier method.
        \item {Capable of reconciling large-scale data (millions of records), both in real-time and \textit{batches}, identifying and correcting errors through reconciliation and adjusting variables to their correct values.}
        \item {Client built with \textbf{TypeScript} and \textbf{React} for better responsiveness, using the \textbf{ReactFlow} library for interaction with nodes.}
        \item {Server developed with API \textit{endpoints}, facilitating integration with other tools and systems.}
        \item {Highly scalable and robust database, implemented with \textbf{PostgreSQL} and \textbf{TimescaleDB} for efficient time series data storage.}
        \item {Technologies Used: Python (Flask), TypeScript (React), PostgreSQL (TimescaleDB).}
      \resumeItemListEnd

       \resumeProject
      { AAICAP - \textit{Artificial Intelligence Correction and Augmentation Pipeline}}
      {Python-based project for correcting pixel-art images generated by Artificial Intelligence.}
      {}

      \resumeItemListStart
        \item {Uses image processing techniques to correct flaws in pixel-art images.}
        \item {Capable of optimizing image quality while preserving relevant characteristics, dynamically adjusting processing parameters.}
        \item {Correction and enhancement pipeline designed for efficient large-scale image processing, with support for automation and API.}
        
        \item {Technologies Used: Python, Flask, OpenCV, PIL.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd
\vspace{-8.5mm}

\section{\textbf{Experience}}
  \resumeSubHeadingListStart
    \resumeSubheading
      { Back-end Development Intern}{On-site}
      {SEMA-MT}{May 2021 - May 2022}
      \vspace{-2.0mm}
      \resumeItemListStart
        \item {Contributed to the development of a field tool using \textbf{C\#} and \textbf{.NET}, designed to collect and manage data in remote environments.}
        \item {Implemented database synchronization functionality, ensuring data consistency both in online and offline modes.}
        \item {Developed and optimized offline functionality, allowing users to continue using the tool without connectivity, with automatic synchronization upon reconnection.}
        \item {Collaborated with the team on integrating the tool with internal and external systems via robust APIs.}
        \item {\textbf{Technologies Used:} C\#, .NET, SQL Server, RESTful APIs.}
      \resumeItemListEnd


    \vspace{-3.0mm}
    
        \resumeSubheading
      { Junior Full Stack Developer}{On-site}
      {PGE-MT}{May 2024 - Present}
      \vspace{-2.0mm}
      \resumeItemListStart
        \item {Implemented automations using \textbf{Google Apps Script} and \textbf{AppSheet}, optimizing internal workflows.}
        \item {Developed systems for managing legal processes and controlling schedules for prosecutors, using \textbf{TypeScript} and \textbf{React} for the front-end, \textbf{PostgreSQL} for the database, and deployed on \textbf{Firebase} with authentication via \textbf{Google Authentication}.}
        \item {Integrated \textbf{ChatGPT} for automatic process summaries and pre-assessment of litispendence, using \textbf{Node.js} and the \textbf{ChatGPT API}.}
        \item {\textbf{Technologies Used:} TypeScript, React, PostgreSQL, Firebase, Node.js, Google Apps Script, AppSheet, ChatGPT API.}
      \resumeItemListEnd

    \vspace{-3.0mm}
  \resumeSubHeadingListEnd
  

\section{\textbf{Technical Skills and Interests}}
\begin{itemize}[leftmargin=0.05in, label={}]
    \small{\item{
     \textbf{Languages:}{ Portuguese (native), English (fluent), Spanish (intermediate), French (beginner), and German (beginner).} \\
     \textbf{Programming Languages:}{ C/C++, Rust, Python, and TypeScript. } \\
     \textbf{Libraries:}{ NumPy, Pandas, ReactJS, and Redux. }\\ 
     \textbf{Tools:}{ Node.js, Git, GitHub, Gitlab, AppScript, and AppSheet. } \\ 
     \textbf{Frameworks:}{ ReactJS, Flask, Express.js, and FastAPI. } \\
     \textbf{Cloud/Databases:}{ Firebase, PostgreSQL, and TimescaleDB. } \\  
    }}
\end{itemize}

\end{document}
