%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Class
% Version 2.0 (12/10/23)
%
% This class originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Omar Roldan
% Based on a template by  Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{multicol}
\setlength{\columnsep}{0mm}
%----------------------------------------------------------------------------------------
\usepackage{lipsum}  


\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\newcommand{\yourName}{Nilton Aguiar dos Santos}
\newcommand{\yourEmail}{nilton.naab@gmail.com}
\newcommand{\yourPhone}{+55 (65) 99278-5635 }
\newcommand{\githubUserName}{notNilton}
\newcommand{\linkedinUserName}{notNilton}

\begin{center}
    \Huge 
    \scshape {\yourName} \\ 
    \vspace{10pt}
    \normalsize 
    \href{mailto:\yourEmail}{\underline{\yourEmail}}
    \enspace $|$ \enspace
    \yourPhone
    \enspace $|$ \enspace
    \href{https://github.com/\githubUserName}{\underline{GitHub/\githubUserName}}
    \enspace $|$ \enspace
    \href{https://www.linkedin.com/in/notnilton/}{\underline{LinkedIn/\linkedinUserName}}

\end{center}

%------ ----------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------


\begin{minipage}[t]{0.55\textwidth}
    \cvsect{Hard Skills}
	\vspace{-6pt}
 
        \textbf{Programming Languages: }{Python, JavaScript, C, C++, C\# and MySQL.}
        
        \vspace{2.5pt}
        
        \textbf{Technologies: }{React, .NET, API Management, Docker, Kubernetes, Excel and PowerBI.}
       
        \vspace{2.5pt}
        
        \textbf{Languages: }{{German: }{B1}, {French: }{B2}, {Portuguese: }{C2} and {English: }{C2}}

\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.40\textwidth}
    \cvsect{Soft Skills}
	\vspace{-6pt}
 
        \textbf{Communication: }{Presentation skills, Written communication.}
        
        \vspace{2.5pt}
        
        \textbf{Teamwork: }{Conflict resolution, Collaboration.}

        \vspace{2.5pt}
        
        \textbf{Creativity: }{Brainstorming, Experimentation, Curiosity.}
\end{minipage}

%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------
% \cvsect{Projects}
% \begin{entrylist}
%     \entry
% 		{Technology}
% 		{My project 1}
% 		{github.com link}
% 		{%Dummy text 
%         \lipsum[1][1-3]}
%     \entry
% 		{Technology}
% 		{My project 2}
% 		{github.com link}
% 		{%Dummy text 
%         \lipsum[1][1-3]}
% 	\entry
% 		{Technology}
% 		{My project 3}
% 		{github.com link}
% 		{%Dummy text 
%         \lipsum[1][1-3]}
%     \entry
% 		{Technology}
% 		{My project 4}
% 		{github.com link}
% 		{%Dummy text 
%         \lipsum[1][1-3]}
% \end{entrylist}
%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Experience}
\begin{entrylist}
	\entry
            {5/19 - 5/20}
		{\normalsize System Assistant}
		{\normalsize Federal University of Mato Grosso}
		{\vspace{-10pt}
        \vspace{2.5pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item {Worked on the transition of a Virtual Machine based infrastructure to a Docker based.}
            \vspace{2.5pt}
            \item {Maintained the Docker infrastructure to be able to offer servers and machines to 1100 concurrent users.}
        \end{itemize} 
        \texttt{Excel} \slashsep \texttt{Docker}}
	\entry
            {11/19 - 11/21}
		{\normalsize Robotics Teacher}
		{\normalsize Federal University of Mato Grosso}
		{\vspace{-10pt}
        \vspace{2.5pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item {I taught basic robotics to high school students in six classes of 35 students each.}
            \vspace{2.5pt}
            \item {The classes were separated into: basic concepts, programming in \textbf{C}, basic 
            concepts of \textbf{physics} focused on robotics and assembly of prototypes using \textbf{electronics fundamentals}.}
            \vspace{2.5pt}
            \item {Each of my class results were presented to my superiors in \textbf{Power BI} presentations.}
        \end{itemize} 
        \texttt{C} \slashsep \texttt{Power BI} \slashsep \texttt{Excel}}
        \entry
		{03/21 - 03/22}
		{\normalsize System Analyst}
		{\normalsize State Secretariat for the Environment of Mato Grosso}
		{\vspace{-10pt}
        \vspace{2.5pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item {I participated in the State Secretariat for the Environment of Mato Grosso systems analysis team, focused on the area in direct contact with customers.}
            \vspace{2.5pt}
            \item {Developed custom tools to client management, and resource allocation using \textbf{Excel}.}
            \vspace{2.5pt}
            \item {I completely automated my work process in which it was necessary to check the current stage on several platforms. Using \textbf{JavaScript} and \textbf{Python} to web scrape those said platforms. The entire result of these processes was documented in \textbf{Power BI} for presentation to my superiors.}
        \end{itemize} 
        \texttt{JavaScript} \slashsep \texttt{Python} \slashsep \texttt{Power BI} \slashsep \texttt{Excel}}
        \entry
		{03/22 - 03/23}
		{\normalsize Developer}
		{\normalsize State Secretariat for the Environment of Mato Grosso}
		{\vspace{-10pt}
        \vspace{2.5pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item {Given my skills, I was offered a position in the solution development team of State Secretariat for the Environment of Mato Grosso.}
            \vspace{2.5pt}
            \item {I developed software using mainly \textbf{C\#} and \textbf{MySQL}  for use in the field by employees of the State Secretariat for the Environment to check the status of each user as well as modify the database, on site.}
            \vspace{2.5pt}
            \item {The software was capable to synchronizing, using \textbf{MySQL} so that whenever the user had network access, so it was always updated with the current status of the database, but also be able to send to the database requests so that the modifications made by the employee was accepted.}
            \vspace{2.5pt}
            \item {This solution completely changed employees' field trips, making them faster, with fewer errors and better legal documentation of decision-making, as the previous projects, my entire progress was documented on \textbf{Power BI} to explain my superiors of the progress made.}
        \end{itemize} 
        \texttt{C\#} \slashsep \texttt{Power BI} \slashsep \texttt{MySQL}}
  %       \entry
		% {02/21 - 06/23}
		% {\normalsize Researcher}
		% {\normalsize Federal University of Mato Grosso}
		% {\vspace{-10pt}
  %       \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
  %           \item {I participated in a Federal University of Mato Grosso research team on a reevaluation of the Tennessee Eastman Process, using a more modern approach, such as a \textbf{Fuzzy Filter}, implementation }
  %           \item {Developed custom tools to client management, and resource allocation using \textbf{Excel}.}
  %           \item {I completely automated my work process in which it was necessary to check the current stage on several platforms. Using \textbf{JavaScript} and \textbf{Python} to web scrape those said platforms. The entire result of these processes was documented in \textbf{Power BI} for presentation to my superiors.}
  %       \end{itemize} 
  %       \texttt{JavaScript} \slashsep \texttt{Python} \slashsep \texttt{Power BI} \slashsep \texttt{Excel}}
        \entry
		{06/23 - Current}
		{\normalsize Developer}
		{\normalsize Federal University of Mato Grosso}
		{\vspace{-10pt}
        \vspace{2.5pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item {I am developing industrial plant process analysis software, using \textbf{JavaScript with React} as a front-end development environment, \textbf{Python} as a back-end solution to the many computations taken of considerations, \textbf{MySQL} as a database, and \textbf{API Management} as a solution to the authentication problem, example.}
            \vspace{2.5pt}
            \item {The main goal of this software solution is to make a data reconciliation and signal behavior prediction and signal behavior solution to a industrial scale situation, all of that while on a web service to be as ease of access as possible.}
        \end{itemize} 
        \texttt{JavaScript} \slashsep \texttt{React} \slashsep \texttt{Python} \slashsep \texttt{MySQL} \slashsep \texttt{API Management}}
\end{entrylist}
%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Education}
\begin{entrylist}
    \entry
		{\normalsize 2018 - 2024}
		{\normalsize Computer Engineering}
		{\normalsize Universidade Federal de Mato Grosso - Cuiabá, MT.}
		{}
\end{entrylist}
\end{document}
